### 2018-04-26 response.tex

\introcomment{~}{%
In addition, I also agree that all the terms and methodology should be well defined for the BSSA readership, so that the paper can be understood by them without resort to frequent online searches.
}

\response{%
\textcolor{red}{[ *** Pending ***]}
% Thanks for the constructive suggestions. We agree with you and peer reviewers that the technical terms are not commonly used in seismology and strong motion earthquake engineering. The confusion happened because of integrating three different topics into a method to carry out this research. One technical term in one field is different in another field and that cause a confusion. For example cluster, class, and label all are referring to the same concept, however, it depends on the application. We added a paragraph in the \textbf{Data Analysis Method} section to elaborate this confusion.
% \vspace{2ex}
% \newline
% We added text to abstract and conclusion to give a heads up to readers about 11 metrics and one earthquake with 3 velocity model  simulations.
}

\introcomment{~}{%
I found Figure 6 very helpful in giving me a very simple if heuristic understanding why C4, C5, C6, and C8 are the most diagnostic of the goodness of fit. It clearly shows that only these metrics are change significantly with the goodness of fit (P, F, G, E). Plotting these values as a function of P, F, G, and E together on the same figure might allow the reader to see this relationship more clearly and might help provide a heuristic understanding of how C4, C5, C6, and C8 are diagnostic whereas C11 is constant with P, F, G, and E, and thus not diagnostic. In fact, in my opinion, Figure 6 is a simple and easy way of determining which metrics are diagnostic that might even eliminate the need for the decision trees. In any case, more discussion of this figure might help the authors make the case for the main conclusions.
}

\response{%
Thank you. This is very true. Figure 6 certainly conveys a clear message about how the metrics vary for each validation classes. The decision tree analysis, nonetheless, is still needed in order to convert this qualitative insight into a set of quantitative conditionals to decide the final class based on the GOF scores. In attention to this comment, we modified Fig.~6 to highlight the boundaries of the categories defined by Anderson (2004) and expanded the text in the Results section to provide a better explanation of the meaning of the results shown in this figure.
}

### 2018-04-26 dataset.tex
making progress

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations. The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}
% 
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and component\myrevision{s} of motion (NS, EW, UD). In each case, the median is indicated by a notch in the box, the boxes represents the interquartile range ($\mathrm{IQR} = \mathrm{Q}3 - \mathrm{Q}1$), and the line shows the range of the data, with outliers (data less than $\mathrm{Q}1 - 1.5 \mathrm{IQR}$ and greater than $\mathrm{Q}3 + 1.5 \mathrm{IQR}$) shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations. The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}
% 
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and component\myrevision{s} of motion (NS, EW, UD). In each case, \change{the boxes represent the interquartile range ($\mathrm{IQR} = \mathrm{Q}3 - \mathrm{Q}1$), the medians are indicated by a notch in the boxes, and the vertical lines show} the range of the data, with outliers (data less than $\mathrm{Q}1 - 1.5 \mathrm{IQR}$ and greater than $\mathrm{Q}3 + 1.5 \mathrm{IQR}$) shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}

### 2018-04-26 metrics.tex
making progress

There are various methods and algorithms available to evaluate the similarity between two or more seismograms, both through direct quantitative comparisons or indirect statistical analysis \citep[e.g.,][]{Anderson_2004_Proc, Kristekova_2006_BSSA, Kristekova_2009_GJI, Olsen_2010_SRL, Burks_BSSA_2014, Rezaeian_2015_BSSA}. In earthquake ground motion simulation, they are primarily used for verification with respect to benchmark or analytical solutions, and for validation with respect to data (i.e., ground motion records). Here, we focus on the list of metrics proposed by \citet{Anderson_2004_Proc}, with an additional metric for duration, as suggested by others \citep{Olsen_2010_SRL, Maufroy_2015_BSSA} and as implemented in \citet{Taborda_2013_BSSA}.

>>>>

There are various methods and algorithms available to evaluate the similarity between two or more seismograms, both through direct \change{signal-to-signal} quantitative comparisons or \change{overall} statistical analysis \citep[e.g.,][]{Anderson_2004_Proc, Kristekova_2006_BSSA, Kristekova_2009_GJI, Olsen_2010_SRL, Burks_BSSA_2014, Rezaeian_2015_BSSA}. In earthquake ground motion simulation, they are primarily used for verification with respect to benchmark or analytical solutions, and for validation with respect to data (i.e., ground motion records). Here, we focus on the list of metrics proposed by \citet{Anderson_2004_Proc}, with an additional metric for duration, as suggested by others \citep{Olsen_2010_SRL, Maufroy_2015_BSSA} and as implemented in \citet{Taborda_2013_BSSA}.

### 2018-04-26 results.tex
making progress

Figure \ref{fig:boxed-clusters} shows the statistical distribution (box-plots) of the samples once the dataset is partitioned into the four GOF validation classes. This is similar to Fig.~\ref{fig:data-box-plot}, but after the clustering process is completed. Separately, we prepared similar plots to look at the influence of the velocity models and components of motions on the results of the clustering process and, as observed before, they had no significant differences with the aggregate of all the samples in the dataset.

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06_mod}
	\caption{Statistical distribution of the dataset as partitioned into the four validation categories (poor, fair, good, excellent) after the clustering analysis. The distributions are shown in the form of box-plots for each metric (C1 through C11). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range, with outliers shown as scattered dots. The color version of this figure is available only in the electronic edition. \myrevision{Dashed lines represent the boundaries of poor, fair, good, and excellent categories according to  \citeauthor{Anderson_2004_Proc}'s method.}}
	\label{fig:boxed-clusters}
\end{figure*}

@@

>>>>

Figure \ref{fig:boxed-clusters} shows the statistical distribution (box-plots) of the samples once the dataset is partitioned into the four GOF validation classes. This is similar to Fig.~\ref{fig:data-box-plot}, but after the clustering process is completed. Separately, we prepared similar plots to look at the influence of the velocity models and components of motions on the results of the clustering process and, as observed before, they had no significant differences with the aggregate of all the samples in the dataset. \change{Figure 6 is particularly important because it highlights the outcome of the clustering process and provides a preview into the decision tree analysis results. Notice that metrics C5 through C8 consistently fall within the poor, fair, good, and excellent classification and that metrics C3 and C4 also show a progressive variation in sync with the validation classes. This means that these metrics are likely the best predictors for the outcome of the validation process, as we will see upon performing the decision tree analysis. On the other hand, metrics C1 and C2, and C9 through C11 are almost invariant, therefore less or not decisive in the validation process. C11, in particular, shows a broader (larger boxes) distribution, which indicates that it is less effective in predicting the final validation class.}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06}
	\caption{Statistical distribution of the dataset as partitioned into the four validation categories (poor, fair, good, excellent) after the clustering analysis. The distributions are shown in the form of box-plots for each metric (C1 through C11). In each case, \change{the medians are indicated by a notch in the boxes of the central quartiles, and the vertical} lines represent the interquartile range, with outliers shown as scattered dots. \change{The dashed lines and background shadows represent the boundaries of the poor, fair, good, and excellent categories as defined by \citet{Anderson_2004_Proc}.} The color version of this figure is available only in the electronic edition.}
	\label{fig:boxed-clusters}
\end{figure*}

@@

\input{tab-partition-extra}
